---
title: "Figure1_EM"
author: "Mike"
---
For plotting single traced neurons to illustrate their polarity. Also the code used to make Figure 1A 

Load up the required packages, functions and the symlink to Google Drive 
```{r, echo=FALSE, results="hide"}
library(here)
library(dplyr)
library(nat)
library(elmr)
library(nat.templatebrains)
library(nat.flybrains)
download_jefferislab_registrations()
set3d <- function(pos = c("front", "left", "back", "right",
                          "ventral", "dorsal"), zoom = 0.7, ...) {
  pos <- match.arg(pos)
  m <- diag(c(1, -1, -1, 1)) # front
  if (pos == "left") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- 1
    m[3, 1] <- 1
  }
  if (pos == "back") {
    m <- diag(c(-1, -1, 1, 1))
  }
  if (pos == "right") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- m[3, 1] <- -1
  }
  if (pos == "ventral") {
    m <- diag(c(1, -1, -1, 1))
  }
  if (pos == "dorsal") {
    m <- diag(c(1, 1, 1, 1))
  }
  4
  view3d(userMatrix = m, zoom = zoom, ...)
}
here()
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/Figure1", here())

```

Load up the data and examine which tracings are available
```{r, echo=FALSE}
emmatches_JFRC2013<-readRDS("Figure1/emmatches_JFRC2013.rds")
celltypes<-select(emmatches_JFRC2013[,],cell.type, Miketype)
celltypes<-mutate(celltypes, index=1:nrow(celltypes))
celltypes
```

Create LH masks in JFRC2013 space
```{r, echo=FALSE}
npmask<-subset(FCWBNP.surf, "LH_L")
npmask.jfrc2013<-xform_brain(x=npmask, sample = FCWB, reference = JFRC2013)
```

List and plot the neurons we are interested in showing as an inset to support the LM polarity data
```{r, echo=FALSE}
Cells2Plot<-c("3A", "116A", "70C")
for(i in 1:length(Cells2Plot)){
    cell<-Cells2Plot[i]
    index<-filter(celltypes, Miketype==cell)$index
    
    clear3d()
    plot3d(emmatches_JFRC2013[[index]], WithConnectors = TRUE, WithNodes = FALSE
           , lwd=2, col="black", soma=TRUE)
    plot3d(npmask.jfrc2013, alpha=0.2)
    #plot3d(JFRC2013, alpha=0.1)
    set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
    snapshot3d(paste0("Figure1/", cell, ".png"))
}
```

To make Figure 1A
```{r, echo=FALSE}
#Sort out the masks
LHmask<-subset(FCWBNP.surf, "LH_R")
LHmask.jfrc2<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2)
CAmask<-subset(FCWBNP.surf, "MB_CA_R")
CAmask.jfrc2<-xform_brain(x=CAmask, sample = FCWB, reference = JFRC2)
ALmask<-subset(FCWBNP.surf, "AL_R")
ALmask.jfrc2<-xform_brain(x=ALmask, sample = FCWB, reference = JFRC2)
DA1.jfrc2<-readRDS("Figure1/da1.jfrc2.rds")
clear3d()
plot3d(JFRC2, alpha=0.2)
plot3d(LHmask.jfrc2, alpha=0.2)
plot3d(CAmask.jfrc2, alpha=0.2, col="green")
plot3d(ALmask.jfrc2, alpha=0.2)
plot3d(DA1.jfrc2, lwd=4, col="black")
snapshot3d("Figure1/F1A.png")
```


