 ---
title: "Figure5"
author: "Mike"
---
#For plotting the heatmaps and running the analyses in Figure5 and FigureS5

First load up the required libraries and functions
```{r, echo=FALSE, results="hide"}
library(here)
library(dplyr)
library(NMF)                # aheatmap()
library(nat)
library(elmr)
library(xlsx)
library(nat.templatebrains)
library(nat.flybrains)
download_jefferislab_registrations()
readin<-function(file) {
  as.matrix(read.table(file, header=TRUE,row.names=1))
} #For reading in the text files containing LM overlap data 
set3d <- function(pos = c("front", "left", "back", "right",
                          "ventral", "dorsal"), zoom = 0.7, ...) {
  pos <- match.arg(pos)
  m <- diag(c(1, -1, -1, 1)) # front
  if (pos == "left") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- 1
    m[3, 1] <- 1
  }
  if (pos == "back") {
    m <- diag(c(-1, -1, 1, 1))
  }
  if (pos == "right") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- m[3, 1] <- -1
  }
  if (pos == "ventral") {
    m <- diag(c(1, -1, -1, 1))
  }
  if (pos == "dorsal") {
    m <- diag(c(1, 1, 1, 1))
  }
  4
  view3d(userMatrix = m, zoom = zoom, ...)
}
here()
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/Figure5", here())
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/FigureS5", here())
```

Plot images of the PLP, GNG (part of SEZ) and the LAL (lateral accessory lobe/posterior antennal lobe), which are the main input dendritic zones for non-canonical LH input 
```{r, echo=FALSE}
clear3d()
LHmask<-subset(FCWBNP.surf, "LH_L")
LHmask.jfrc2013<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2013)
npmask<-subset(FCWBNP.surf, "AVLP_L")
npmask.jfrc2013<-xform_brain(x=npmask, sample = FCWB, reference = JFRC2013)
plot3d(npmask.jfrc2013, alpha=0.2, col="green")
plot3d(LHmask.jfrc2013, alpha=0.2, col="red")
plot3d(JFRC2013, alpha=0.15)
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("Figure5/AVLP.png")
```

Load up the LHON dendrite x PN axon overlap data and plot it for the supplementary figure S5. 
```{r, echo=FALSE}
LHON_PN<-readin("FigureS5/Output_den_x_Mask_PN_PN.txt")

#To rename the LH cell-types
NAmaster<-read.xlsx(file="/Users/dolanm/Dropbox/JFRCvisitorProject/Neuroanatomy_Master.xlsx", sheetIndex = 1)
LHnewnames<-select(NAmaster,LHClusters., FinalNames)

oldnames<-lapply(X = dimnames(LHON_PN), FUN = gsub, pattern = "CellType_", replacement = "", fixed = TRUE)
oldname1<-data.frame(oldnames=oldnames[[1]]) #For the row names
oldname1<-merge(x=oldname1, by.x ="oldnames", y=LHnewnames, by.y = "LHClusters.", sort =FALSE)
newname1<-as.character(oldname1$FinalNames)

dimnames(LHON_PN)<-list(newname1, dimnames(LHON_PN)[[2]])
aheatmap(x = LHON_PN, filename=paste0("FigureS5/LHON_PN.pdf")
         ,fontsize = 9, cexRow = 1, cexCol = 2, Colv = FALSE, treeheight = 15, col="black")
```

LH gets other inputs in addition to the projection neurons. Load up the Input data, including taste and temperature PN data using lines identified in other studies.  
```{r, echo=FALSE}
LHON_input<-t(readin("Figure5/Output_den_x_LHIN_axonmemb.txt"))
```

Next want to remove unwanted/unclear cell-types from the input designation and add modality tracts to the LHON_input heatmap. 
```{r, echo=FALSE}
#celltype_remove<-c("145", "PN1", "PN2",  )
#write.xlsx(x = dimnames(LHON_input)[[2]], file = "Figure5/LHON_Input_tracks.xlsx")
#subset(LHON_input, colnames(LHON_input)!="CellType_29A")  

modality<-read.xlsx(file = "Figure5/LHON_Input_tracks.xlsx", sheetIndex = 1)

dimnames(LHON_input)<-list(newname1,modality$newname)
aheatmap(x = LHON_input, filename=paste0("Figure5/LHON_input.pdf")
         , annCol  = modality$Modality, col="black", annColors = "rainbow", annLegend = FALSE
         ,fontsize = 10, cexRow = 2, cexCol = 0.6, Colv = FALSE, treeheight = 8)
```

Combine all the LH input (PN, TPN, Visual, Taste etc) to identify LHONs that integrate olfactory and temperature data and two view the different clusters of inputs to the LH 
```{r, echo=FALSE}
LHIN_all<-cbind(LHON_PN, LHON_LHIN)
aheatmap(x = LHIN_all, filename=paste0("Figure5/LHON_LHIN_PN.pdf")
         ,fontsize = 10, cexRow = 2, cexCol = 0.6,  treeheight = 8)
```

For supplementary, plot heatmaps of the LHLN and PNs
```{r, echo=FALSE}
LHLNs_PNs<-readin(file = "FigureS5/Local_memb_x_Mask_PN_PN.txt")

#Calculate the LHLN new names
oldnames<-lapply(X = dimnames(LHLNs_PNs), FUN = gsub, pattern = "CellType_", replacement = "", fixed = TRUE)
oldname2<-data.frame(oldnames=oldnames[[1]]) #For the row names
oldname2<-merge(x=oldname2, by.x ="oldnames", y=LHnewnames, by.y = "LHClusters.", sort =FALSE)
newname2<-as.character(oldname2$FinalNames)

dimnames(LHLNs_PNs)[[1]]<-newname2
aheatmap(x = LHLNs_PNs, filename=paste0("FigureS5/LHLNs_PNs.pdf")
         ,fontsize = 9, cexRow =1.5, cexCol =5, col="black", treeheight = 8,
         , cellwidth = 16,Colv = FALSE)
```

For the supplementary information, plot heatmaps of the MBON axons versus LHON dendrites 
```{r, echo=FALSE}
LHONden_MBON<-readin(file = "FigureS5/Output_den_x_MBON_axon.txt")
dimnames(LHONden_MBON)<-list(newname1, gsub(dimnames(LHONden_MBON)[[2]], pattern = "CellType_", replacement = ""))
aheatmap(x = LHONden_MBON, filename=paste0("FigureS5/LHONden_MBON.pdf")
         ,fontsize = 10, cexRow = 3, cexCol = 0.65, col="black", treeheight = 12, Colv = FALSE)
```

For the supplementary information, plot heatmaps of the MBON axons versus LHLNs
```{r, echo=FALSE}
LHLN_MBON<-readin(file = "FigureS5/Local_memb_x_MBON_axon.txt")
aheatmap(x = LHLN_MBON, filename=paste0("Figure6/LHLN_MBON.pdf")
         ,fontsize = 10, cexRow = 0.8, cexCol = 0.65, treeheight = 12, Colv = FALSE)
```


```{r, echo=FALSE}
```


