---
title: "Figure6"
author: "Mike"
---
#Figure6 Plotting 
Code to plot the MBON and DAN heatmaps, for both Figure6A/B and the supplementary information

First load up the required libraries and functions
```{r, echo=FALSE, results="hide"}
library(here)
library(dplyr)
library(xlsx)
library(NMF)                # aheatmap()
library(ggplot2)
readin<-function(file) {
  as.matrix(read.table(file, header=TRUE,row.names=1))
}
here()
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/Figure6", here())
```

Load and plot the overlap analysis of LHON axons and MBON Axons  
```{r, echo=FALSE}
LHON_MBON<-readin(file = "Figure6/Output_axonmemb_x_MBON_axon.txt")
aheatmap(x = LHON_MBON, filename=paste0("Figure6/LHON_MBON.pdf")
         ,fontsize = 10, cexRow = 3, cexCol = 0.65, treeheight = 12, Colv = FALSE)
```

Load and plot the overlap analysis of LHON axons and DAN dendrites 
```{r, echo=FALSE}
LHON_DAN<-readin(file = "Figure6/Output_axonmemb_x_DAN_den.txt")
aheatmap(x = LHON_DAN, filename=paste0("Figure6/LHON_DAN.pdf")
         ,fontsize = 10, cexRow = 3, cexCol = 0.65, treeheight = 12, Colv = FALSE)
```

For the supplementary information, plot heatmaps of the MBON axons versus LHON dendrites 
```{r, echo=FALSE}
LHONden_MBON<-readin(file = "Figure6/Output_den_x_MBON_axon.txt")
aheatmap(x = LHONden_MBON, filename=paste0("Figure6/LHONden_MBON.pdf")
         ,fontsize = 10, cexRow = 3, cexCol = 0.65, treeheight = 12, Colv = FALSE)
```

For the supplementary information, plot heatmaps of the MBON axons versus LHLNs
```{r, echo=FALSE}
LHLN_MBON<-readin(file = "Figure6/Local_memb_x_MBON_axon.txt")
aheatmap(x = LHLN_MBON, filename=paste0("Figure6/LHLN_MBON.pdf")
         ,fontsize = 10, cexRow = 0.8, cexCol = 0.65, treeheight = 12, Colv = FALSE)
```

For the supplementary information, plot heatmaps of the MBON axons versus the LHINs 
```{r, echo=FALSE}


```

```{r, echo=FALSE}


```

```{r, echo=FALSE}


```





