---
title: "Figure1_EM"
author: "Mike"
---
For plotting single traced neurons to illustrate their polarity. Also the code used to make Figure 1A and Figure S1.

Load up the required packages, functions and the symlink to Google Drive 
```{r, echo=FALSE, results="hide"}
library(here)
library(dplyr)
library(nat)
library(elmr)
library(catmaid)
library(nat.templatebrains)
library(nat.flybrains)
download_jefferislab_registrations()
set3d <- function(pos = c("front", "left", "back", "right",
                          "ventral", "dorsal"), zoom = 0.7, ...) {
  pos <- match.arg(pos)
  m <- diag(c(1, -1, -1, 1)) # front
  if (pos == "left") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- 1
    m[3, 1] <- 1
  }
  if (pos == "back") {
    m <- diag(c(-1, -1, 1, 1))
  }
  if (pos == "right") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- m[3, 1] <- -1
  }
  if (pos == "ventral") {
    m <- diag(c(1, -1, -1, 1))
  }
  if (pos == "dorsal") {
    m <- diag(c(1, 1, 1, 1))
  }
  4
  view3d(userMatrix = m, zoom = zoom, ...)
}
here()
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/Figure1", here())

```

Load up the data and examine which tracings are available
```{r, echo=FALSE}
emmatches_JFRC2013<-readRDS("Figure1/emmatches_JFRC2013.rds")
celltypes<-select(emmatches_JFRC2013[,],cell.type, Miketype)
celltypes<-mutate(celltypes, index=1:nrow(celltypes))
celltypes
```

Create LH masks in JFRC2013 space
```{r, echo=FALSE}
npmask<-subset(FCWBNP.surf, "LH_L")
npmask.jfrc2013<-xform_brain(x=npmask, sample = FCWB, reference = JFRC2013)
```

List and plot the neurons we are interested in showing as an inset to support the LM polarity data
```{r, echo=FALSE}
Cells2Plot<-c("3A", "116A", "70C")
for(i in 1:length(Cells2Plot)){
    cell<-Cells2Plot[i]
    index<-filter(celltypes, Miketype==cell)$index
    clear3d()
    plot3d(emmatches_JFRC2013[[index]], WithConnectors = FALSE, WithNodes = FALSE
           , lwd=2, col="black", soma=TRUE)
    plot3d(npmask.jfrc2013, alpha=0.2)
    #Add the custom, bigger connectors (plot3d's representations are too small)
    synapses<-connectors(emmatches_JFRC2013[[index]])
    presynapses<-filter(synapses, prepost==0)
    postsynapses<-filter(synapses, prepost==1)
    spheres3d(xyzmatrix(presynapses), col="red", radius = 1)
    spheres3d(xyzmatrix(postsynapses), col="cyan", radius = 1)
    #plot3d(JFRC2013, alpha=0.1)
    set3d("front", 0.7, zoom = 0.7) #Function that sets the angle and zoom 
    snapshot3d(paste0("Figure1/", cell, ".png"))
}
```

To make Figure 1A
```{r, echo=FALSE}
#Sort out the masks
LHmask<-subset(FCWBNP.surf, "LH_L")
LHmask.jfrc2<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2)
CAmask<-subset(FCWBNP.surf, "MB_CA_L")
CAmask.jfrc2<-xform_brain(x=CAmask, sample = FCWB, reference = JFRC2)
ALmask<-subset(FCWBNP.surf, "AL_L")
ALmask.jfrc2<-xform_brain(x=ALmask, sample = FCWB, reference = JFRC2)
DA1.jfrc2<-readRDS("Figure1/da1.jfrc2.rds")
DA1.jfrc2<-mirror_brain(DA1.jfrc2, brain=JFRC2, mirrorAxis = "X", transform = "warp")
clear3d()
plot3d(JFRC2, alpha=0.2)
plot3d(LHmask.jfrc2, alpha=0.2)
plot3d(CAmask.jfrc2, alpha=0.2, col="green")
plot3d(ALmask.jfrc2, alpha=0.2)
plot3d(DA1.jfrc2, lwd=4, col="black")
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("Figure1/F1A.png")
```

Code to make a projection of all the tracings for the supplementary information Figure S1
```{r, echo=FALSE}
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/FigureS1", here())
clear3d()
plot3d(emmatches_JFRC2013, lwd=2, soma=T)
plot3d(JFRC2013, alpha=0.1)
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("FigureS1/allEMtracings.png")

```
