---
title: "Figure4"
author: "Mike"
---
#For plotting the heatmaps and brain regions in Figure 4

First load up the required libraries and functions
```{r, echo=FALSE, results="hide"}
library(here)
library(dplyr)
library(NMF)                # aheatmap()
library(nat)
library(elmr)
library(xlsx)
library(nat.templatebrains)
library(nat.flybrains)
download_jefferislab_registrations()
readin<-function(file) {
  as.matrix(read.table(file, header=TRUE,row.names=1))
} #For reading in the text files containing LM overlap data 
set3d <- function(pos = c("front", "left", "back", "right",
                          "ventral", "dorsal"), zoom = 0.7, ...) {
  pos <- match.arg(pos)
  m <- diag(c(1, -1, -1, 1)) # front
  if (pos == "left") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- 1
    m[3, 1] <- 1
  }
  if (pos == "back") {
    m <- diag(c(-1, -1, 1, 1))
  }
  if (pos == "right") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- m[3, 1] <- -1
  }
  if (pos == "ventral") {
    m <- diag(c(1, -1, -1, 1))
  }
  if (pos == "dorsal") {
    m <- diag(c(1, 1, 1, 1))
  }
  4
  view3d(userMatrix = m, zoom = zoom, ...)
}
here()
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/Figure4", here())
```

Plot the SLP and the LH 
```{r, echo=FALSE}
clear3d()
LHmask<-subset(FCWBNP.surf, "LH_L")
LHmask.jfrc2013<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2013)
SLPmask<-subset(FCWBNP.surf, "SLP_L")
SLPmask.jfrc2013<-xform_brain(x=SLPmask, sample = FCWB, reference = JFRC2013)
plot3d(SLPmask.jfrc2013, alpha=0.2, col="magenta")
plot3d(LHmask.jfrc2013, alpha=0.2, col="red")
plot3d(JFRC2013, alpha=0.15)
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("Figure4/SLP.png")
```

Plot the SIP and the LH 
```{r, echo=FALSE}
clear3d()
LHmask<-subset(FCWBNP.surf, "LH_L")
LHmask.jfrc2013<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2013)
SLPmask<-subset(FCWBNP.surf, "SIP_L")
SLPmask.jfrc2013<-xform_brain(x=SLPmask, sample = FCWB, reference = JFRC2013)
plot3d(SLPmask.jfrc2013, alpha=0.2, col="green")
plot3d(LHmask.jfrc2013, alpha=0.2, col="red")
plot3d(JFRC2013, alpha=0.15)
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("Figure4/SIP.png")
```

Plot the SMP and the LH 
```{r, echo=FALSE}
clear3d()
LHmask<-subset(FCWBNP.surf, "LH_L")
LHmask.jfrc2013<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2013)
SLPmask<-subset(FCWBNP.surf, "SMP")
SLPmask.jfrc2013<-xform_brain(x=SLPmask, sample = FCWB, reference = JFRC2013)
plot3d(SLPmask.jfrc2013, alpha=0.2, col="cyan")
plot3d(LHmask.jfrc2013, alpha=0.2, col="red")
plot3d(JFRC2013, alpha=0.15)
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("Figure4/SMP.png")
```

Pull up the new nomenclature and the NTs for LHONs
```{r, echo=FALSE}
LHON_LHONs<-readin("Figure4/Output_axonmemb_x_Output_axonmemb.txt")
NAmaster<-read.xlsx(file="/Users/dolanm/Dropbox/JFRCvisitorProject/Neuroanatomy_Master.xlsx", sheetIndex = 1)
LHnts<-select(NAmaster,LHClusters., Neurotransmitter)
LHnewnames<-select(NAmaster,LHClusters., FinalNames)

#To rename the LH cell-types
oldnames<-lapply(X = dimnames(LHON_LHONs), FUN = gsub, pattern = "CellType_", replacement = "", fixed = TRUE)
oldname1<-data.frame(oldnames=oldnames[[1]]) #For the row names
oldname1<-merge(x=oldname1, by.x ="oldnames", y=LHnewnames, by.y = "LHClusters.", sort =FALSE)
newname1<-as.character(oldname1$FinalNames)

#For LHON neurotransmitters
LHONs<-dimnames(LHON_LHONs)[[1]] #Pull in the cell-types in question and get their order 
LHONs<-data.frame(Type=LHONs)
LHnts$LHClusters.<-paste0("CellType_", LHnts$LHClusters.) #Add CellType to all the names to match them with left_join, remove this 
names(LHnts)<-c("Type", "Neurotransmitter")
LHONtransmitter<-left_join(x = LHONs, y = LHnts, "Type")
LHONtransmitter<-data.frame(Neurotransmitter=as.character(LHONtransmitter$Neurotransmitter))

#Define the colours for annotations 
transmitter_col<-c("red", "dodgerblue", "forestgreen", "dark magenta", "gold", "grey")
names(transmitter_col)<-c("Acetylcholine", "GABA", "Glutamate", "Acetylcholine, GABA",  "Acetylcholine, Glutamate", "GABA, Dopamine" )
```

Calculate the major neuropil output zone as a track for the LHONxLHON heatmap. This is an optional add-on, I didn't like the way it looked
```{r, echo=FALSE}
LHON_nc82<-readin(file = "FigureS4/Output_axonmemb_x_nc82_nc82.txt")
main_np<-data.frame(Type=dimnames(LHON_nc82)[[1]], main_np=NA)
for(i in 1:nrow(LHON_nc82)) {
  type<-row.names(LHON_nc82)[i]
  row<-LHON_nc82[i,]
  row<-data.frame(neuropil=names(row), values=row)
  main_np[i,2]<-as.character(row[which.max(row$values), ]$neuropil)
  } #Calculate the max neuropil for each cell-type 
LHON_np<-data.frame(Output=main_np$main_np)


```

For plotting the overlap analysis of LHONs by LHONs, with modified matrix presentation and NT information. Note remove the 29A modification when I rerun everything with the final dataset
```{r, echo=FALSE}
LHON_LHON<-readin("Figure4/Output_axonmemb_x_Output_axonmemb.txt")
diag(LHON_LHON)<--1

dimnames(LHON_LHON)<-list(newname1, newname1)
#LHON_LHON<-subset(LHON_LHON, colnames(LHON_LHON)!="CellType_29A")
#LHON_LHON<-LHON_LHON[,-23]
aheatmap(x = LHON_LHON, filename=paste0("Figure4/LHON_LHON.pdf")
         ,fontsize = 9, col="black", cexRow = 1, cexCol =1, Rowv = FALSE, treeheight = 10 
         ,annRow = LHONtransmitter, annCol = LHONtransmitter
         ,annColors = list(transmitter_col), annLegend = FALSE)
```

For plotting the overlap analysis of LHON dendrites and local LH neurons with NT annotation tracks 
```{r, echo=FALSE}
LHON_LHLN<-readin("Figure4/Local_memb_x_Output_den.txt")
#Redefine the colours for annotations 
transmitter_col<-c("red", "dodgerblue", "forestgreen", "dark magenta", "gold", "grey")
names(transmitter_col)<-c("Acetylcholine", "GABA", "Glutamate", "Acetylcholine, GABA",  "Acetylcholine, Glutamate", "GABA, Dopamine" )

#For LHONs 
LHONs<-dimnames(LHON_LHLN)[[2]] #Pull in the cell-types in question and get their order 
LHONs<-data.frame(Type=LHONs)
LHnts$LHClusters.<-paste0("CellType_", LHnts$LHClusters.) #Add CellType to all the names to match them with left_join, remove this 
names(LHnts)<-c("Type", "Neurotransmitter")
LHONtransmitter<-left_join(x = LHONs, y = LHnts, "Type")
LHONtransmitter<-data.frame(Neurotransmitter=as.character(LHONtransmitter$Neurotransmitter))

#For the LHLNs 
LHLNs<-dimnames(LHON_LHLN)[[1]] #Pull in the cell-types in question and get their order 
LHLNs<-data.frame(Type=LHLNs)
LHLNtransmitter<-left_join(x = LHLNs, y = LHnts, "Type")
LHLNtransmitter<-data.frame(Neurotransmitter=as.character(LHLNtransmitter$Neurotransmitter))

#Calculate the LHLN new names
oldnames<-lapply(X = dimnames(LHON_LHLN), FUN = gsub, pattern = "CellType_", replacement = "", fixed = TRUE)
oldname2<-data.frame(oldnames=oldnames[[1]]) #For the row names
oldname2<-merge(x=oldname2, by.x ="oldnames", y=LHnewnames, by.y = "LHClusters.", sort =FALSE)
newname2<-as.character(oldname2$FinalNames)

dimnames(LHON_LHLN)<-list(newname2, newname1)
#Plot the heatmap
aheatmap(x = LHON_LHLN, filename="Figure4/LHON_LHLN.pdf"
         ,fontsize = 10, cexRow = .8, cexCol = 5.3, treeheight = 10, col="black"
         ,annRow = LHLNtransmitter, annCol = LHONtransmitter, annColors = list(transmitter_col), annLegend = FALSE)
```

