---
title: "Figure4"
author: "Mike"
---
#For plotting the heatmaps and brain regions in Figure 4

First load up the required libraries and functions
```{r, echo=FALSE, results="hide"}
library(here)
library(dplyr)
library(NMF)                # aheatmap()
library(nat)
library(elmr)
library(xlsx)
library(nat.templatebrains)
library(nat.flybrains)
download_jefferislab_registrations()
readin<-function(file) {
  as.matrix(read.table(file, header=TRUE,row.names=1))
} #For reading in the text files containing LM overlap data 
set3d <- function(pos = c("front", "left", "back", "right",
                          "ventral", "dorsal"), zoom = 0.7, ...) {
  pos <- match.arg(pos)
  m <- diag(c(1, -1, -1, 1)) # front
  if (pos == "left") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- 1
    m[3, 1] <- 1
  }
  if (pos == "back") {
    m <- diag(c(-1, -1, 1, 1))
  }
  if (pos == "right") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- m[3, 1] <- -1
  }
  if (pos == "ventral") {
    m <- diag(c(1, -1, -1, 1))
  }
  if (pos == "dorsal") {
    m <- diag(c(1, 1, 1, 1))
  }
  4
  view3d(userMatrix = m, zoom = zoom, ...)
}
here()
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/Figure4", here())
```

Plot the SLP and the LH 
```{r, echo=FALSE}
clear3d()
LHmask<-subset(FCWBNP.surf, "LH_L")
LHmask.jfrc2013<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2013)
SLPmask<-subset(FCWBNP.surf, "SLP_L")
SLPmask.jfrc2013<-xform_brain(x=SLPmask, sample = FCWB, reference = JFRC2013)
plot3d(SLPmask.jfrc2013, alpha=0.2, col="magenta")
plot3d(LHmask.jfrc2013, alpha=0.2, col="red")
plot3d(JFRC2013, alpha=0.15)
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("Figure4/SLP.png")
```

Plot the SIP and the LH 
```{r, echo=FALSE}
clear3d()
LHmask<-subset(FCWBNP.surf, "LH_L")
LHmask.jfrc2013<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2013)
SLPmask<-subset(FCWBNP.surf, "SIP_L")
SLPmask.jfrc2013<-xform_brain(x=SLPmask, sample = FCWB, reference = JFRC2013)
plot3d(SLPmask.jfrc2013, alpha=0.2, col="green")
plot3d(LHmask.jfrc2013, alpha=0.2, col="red")
plot3d(JFRC2013, alpha=0.15)
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("Figure4/SIP.png")
```

Plot the SMP and the LH 
```{r, echo=FALSE}
clear3d()
LHmask<-subset(FCWBNP.surf, "LH_L")
LHmask.jfrc2013<-xform_brain(x=LHmask, sample = FCWB, reference = JFRC2013)
SLPmask<-subset(FCWBNP.surf, "SMP")
SLPmask.jfrc2013<-xform_brain(x=SLPmask, sample = FCWB, reference = JFRC2013)
plot3d(SLPmask.jfrc2013, alpha=0.2, col="cyan")
plot3d(LHmask.jfrc2013, alpha=0.2, col="red")
plot3d(JFRC2013, alpha=0.15)
set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
snapshot3d("Figure4/SMP.png")
```

Pull up the NTs for LHONs and LHLNs, using the standard colourscheme 
```{r, echo=FALSE}
LHON_LHLN<-readin("Figure4/Local_memb_x_Output_den.txt")
LHnts<-read.xlsx(file="/Users/dolanm/Dropbox/JFRCvisitorProject/Neuroanatomy_Master.xlsx", sheetIndex = 1)
LHnts<-select(LHnts,LHClusters., Neurotransmitter)
#For LHONs 
LHONs<-dimnames(LHON_LHLN)[[2]] #Pull in the cell-types in question and get their order 
LHONs<-data.frame(Type=LHONs)
LHnts$LHClusters.<-paste0("CellType_", LHnts$LHClusters.) #Add CellType to all the names to match them with left_join, remove this 
names(LHnts)<-c("Type", "Neurotransmitter")
LHONtransmitter<-left_join(x = LHONs, y = LHnts, "Type")
LHONtransmitter<-data.frame(Neurotransmitter=as.character(LHONtransmitter$Neurotransmitter))

#For the LHLNs 
LHLNs<-dimnames(LHON_LHLN)[[1]] #Pull in the cell-types in question and get their order 
LHLNs<-data.frame(Type=LHLNs)
LHLNtransmitter<-left_join(x = LHLNs, y = LHnts, "Type")
LHLNtransmitter<-data.frame(Neurotransmitter=as.character(LHLNtransmitter$Neurotransmitter))

#Define the colours for annotations 
transmitter_col<-c("red", "dodgerblue", "forestgreen", "dark magenta", "gold", "grey")
names(transmitter_col)<-c("Acetylcholine", "GABA", "Glutamate", "Acetylcholine, GABA",  "Acetylcholine, Glutamate", "GABA, Dopamine" )
```

For plotting the overlap analysis of LHON dendrites and local LH neurons  
```{r, echo=FALSE}
aheatmap(x = LHON_LHLN, filename="Figure4/LHON_LHLN.pdf"
         ,fontsize = 9, cexRow = 2, cexCol = 5.3, treeheight = 10, col="black"
         ,annRow = LHLNtransmitter, annCol = LHONtransmitter, annColors = list(transmitter_col), annLegend = FALSE)
```

For plotting the overlap analysis of LHONs by LHONs, with modified matrix presentation and NT information. Note remove the 29A modification when I rerun everything with the final dataset
```{r, echo=FALSE}
LHON_LHON<-readin("Figure4/Output_axonmemb_x_Output_axonmemb.txt")
diag(LHON_LHON)<--1

#LHON_LHON<-subset(LHON_LHON, colnames(LHON_LHON)!="CellType_29A")
#LHON_LHON<-LHON_LHON[,-23]
aheatmap(x = LHON_LHON, filename=paste0("Figure4/LHON_LHON.pdf")
         ,fontsize = 9, col="black", cexRow = 1, cexCol = 1, Rowv = FALSE, treeheight = 15 
         ,annRow = LHONtransmitter, annCol = LHONtransmitter, annColors = list(transmitter_col),annLegend = FALSE)
```

