---
title: "Figure2"
author: "Mike"
---
#Figure2 Plotting 
Code to plot the NT profiles of LHONs and fetch their EM skeletons for figure generation

First load up the required libraries and functions
```{r, echo=FALSE, results="hide"}
library(here)
library(dplyr)
library(nat)
library(xlsx)
library(elmr)
library(nat.templatebrains)
library(nat.flybrains)
download_jefferislab_registrations()
set3d <- function(pos = c("front", "left", "back", "right",
                          "ventral", "dorsal"), zoom = 0.7, ...) {
  pos <- match.arg(pos)
  m <- diag(c(1, -1, -1, 1)) # front
  if (pos == "left") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- 1
    m[3, 1] <- 1
  }
  if (pos == "back") {
    m <- diag(c(-1, -1, 1, 1))
  }
  if (pos == "right") {
    m <- diag(c(0, -1, 0, 1))
    m[1, 3] <- m[3, 1] <- -1
  }
  if (pos == "ventral") {
    m <- diag(c(1, -1, -1, 1))
  }
  if (pos == "dorsal") {
    m <- diag(c(1, 1, 1, 1))
  }
  4
  view3d(userMatrix = m, zoom = zoom, ...)
}
here()
file.symlink("/Users/dolanm/Google Drive/SplitGAL4_Paper/Figures/Figure2", here())
```

Load up the EM skeletons (in JFRC2013 space) and plot the cell-types that have a skeleton attached. Note that this dataset comes with significant metadata. Then load up a list of all the LHONs (in a spreadsheet file creating during figuremaking)   
```{r, echo=FALSE}
EMmatches<-readRDS(file = "Figure2/emmatches_JFRC2013.rds")
celltypes<-data.frame(EMmatches[, c(1,3)], 1:nrow(EMmatches[,]))
names(celltypes)<-c("celltype", "Miketype", "index")
LHONs<-read.xlsx(file = "Figure2/Figure2_supp_info.xlsx", sheetIndex = 1)[,1:2]
```

For each cell-type listed as an LHON, plot the corresponding skeleton and save to the figure directory 
```{r, echo=FALSE}
npmask<-subset(FCWBNP.surf, "LH_L")
npmask.jfrc2013<-xform_brain(x=npmask, sample = FCWB, reference = JFRC2013)
Cells2Plot<-LHONs$Cell.Type..old.name.
for(i in 1:length(Cells2Plot)){
    cell<-Cells2Plot[i]
    index<-filter(celltypes, Miketype==cell)$index
    if(length(index)==0) next
    clear3d()
    plot3d(EMmatches[[index[1]]], WithConnectors = FALSE, WithNodes = FALSE
           , lwd=2, col="black", soma=FALSE)
    plot3d(npmask.jfrc2013, alpha=0.2)
    #plot3d(JFRC2013, alpha=0.1)
    set3d("front", 0.7, zoom = 0.8) #Function that sets the angle and zoom 
    snapshot3d(paste0("Figure2/", cell, ".png"))
}
```
